Proposal for Analyzing Language Models: Separatablity of Syntax and Semantics

### 2022-04-27 proposal/proposal.tex
adding due dates to timetable

\section{Divsion of Labor and Timeline}
\label{sec:management}
There are three main parts of this project, coding the experiment, presenting related topics in class and writing the final paper. Each part has detailed requirements and been assigned to a member to take charge of as presented in table \ref{role description}. It is hard to anticipate the time consumed and difficulty of each task. We have set up a regular weekly meeting to update the progress of each part weekly so that everyone is on the same page with the development of the project.

\begin{table*}[ht]
    \centering
    \begin{tabular}{llll}
    \hline
    \textbf{Duty} & \textbf{Details} & \textbf{Who is in Charge} \\
    \hline
    \multirow{5}{*}{Coding the experiment} & data preprocessing & Qingxia \\
    & building probing system \& INLP & Saiya \& Qingxia \\
    & building evaluation system & Gladys \\
    & merging subparts together & Saiya\\ 
    & running different task pairs & Saiya \\
    \hline
    \multirow{2}{*}{Presenting related topic} & \multirow{2}{*}{presenting INLP method} & \multirow{2}{*}{Lindsay \& Gladys} \\
    & & \\
    \hline
    \multirow{3}{*}{Writing paper} & method section  & Lindsay \\
     & result section & Saiya  \\
     & discussion/conclusion section & all\\
    \hline
    \end{tabular}
    \caption{\label{role description} Role Description
    }
    \end{table*}

>>>>

\section{Divsion of Labor and Timeline}
\label{sec:management}
There are three main parts of this project, coding the experiment, presenting related topics in class and writing the final paper. Each part has detailed requirements along with due dates and been assigned to a member to take charge of as presented in table \ref{role description}. It is hard to anticipate the time consumed and difficulty of each task, so all the due dates are not final. We have set up a regular weekly meeting to update the progress of each part weekly so that everyone is on the same page with the development of the project.

\begin{table*}[ht]
    \centering
    \begin{tabular}{llll}
    \hline
    \textbf{Duty} & \textbf{Details} & \textbf{Who is in Charge} &\textbf{Due} \\
    \hline
    \multirow{5}{*}{Coding the experiment} & data preprocessing & Qingxia & 05/04 \\
    & building probing system \& INLP & Saiya \& Qingxia & 05/25 \\
    & building evaluation system & Gladys & 05/25 \\
    & merging subparts together & Saiya & 06/02\\ 
    & running different task pairs & Saiya & 06/02\\
    \hline
    \multirow{2}{*}{Presenting related topic} & \multirow{2}{*}{presenting INLP method} & \multirow{2}{*}{Lindsay \& Gladys} & \multirow{2}{*}{05/11}\\
    & & & \\
    \hline
    \multirow{3}{*}{Writing paper} & method section  & Lindsay & \multirow{3}{*}{06/09}  \\
     & result section & Saiya &  \\
     & discussion/conclusion section & all & \\
    \hline
    \end{tabular}
    \caption{\label{role description} Role Description
    }
    \end{table*}
